### 2022-03-10 introduction/introduction.tex
more

\paragraph{Our Approach} To improve the automatic reasoning for higher-order
logic, we decided not to start from a blank slate and build a new theorem prover.
Rather, we start from a position of strength --- from the state-of-the-art
first-order superposition theorem prover E \cite{scv-19-e23} --- and extend it to higher-order logic. In this way, the points \ref{it:fo} and
\ref{it:size} from the above wishlist are already fulfilled, as E is very
efficient and deals well with large problems.

>>>>

\paragraph{Our Approach} To improve the automatic reasoning for higher-order
logic, we decided not to start from a blank slate and build a new theorem prover.
Rather, we start from a position of strength---from the state-of-the-art
first-order superposition theorem prover E~\cite{scv-19-e23}---and extend it to higher-order logic. In this way, the points \ref{it:fo} and
\ref{it:size} from the above wishlist are already fulfilled, as E is very
efficient and deals well with large problems.

### 2022-03-10 pre/pre.tex
more

>>>>

\subsection{Higher-Order Superposition Calculi}
\label{sec:pre:ho-sup-calculi}

\looseness=-1
In Chapter \ref{ch:intro} we mention that we identified three steps on the road
to extending efficient superposition provers to higher-order logic. Together with
our colleagues we did the necessary theoretical work by extending the superposition
calculus using the same roadmap:

\begin{enumerate}
    \item Bentkamp, Blanchette, Cruanes, and Waldmann designed a complete
    superposition calculus for higher-order logic devoid of
    $\lambda$-abstraction and first-class Booleans \cite{bbcw-21-lfho}. We call
    this calculus \lfsup{}.
    \item Alexander Bentkamp, Blanchette, Tourret,  Vukmirović, and Waldmann
    extended this calculus to support $\lambda$-abstraction
    \cite{bbtvw-21-sup-lam}. We call it \lsup{}.
    \item Bentkamp, Blanchette, Tourret, and Vukmirovi\'c extended \lsup{} with
    support for first-class Booleans \cite{bbtv-21-full-ho-sup}. This amounts to
    designing the complete calculus for full higher-order logic. We call this
    calculus \osup{}.
\end{enumerate}
